The state learner -- a super learner for right-censored data

### 2024-05-14 tex/jrss-version/state-learner-jrss-style.tex
separate figures

%%%CONTEMPORARY%%%
% \documentclass[unnumsec,webpdf,contemporary,large]{oup-authoring-template}%
\documentclass[unnumsec,webpdf,contemporary,large,namedate]{oup-authoring-template}% uncomment this line for author year citations and comment the above
%\documentclass[unnumsec,webpdf,contemporary,medium]{oup-authoring-template}
%\documentclass[unnumsec,webpdf,contemporary,small]{oup-authoring-template}

@@

% \usepackage[tablesonly,heads,nolists]{endfloat}

@@

%% Toggle with or without figures
% \def\nofig{1}

>>>>

%%%CONTEMPORARY%%%
% \documentclass[unnumsec,webpdf,contemporary,large]{oup-authoring-template}%
\documentclass[numsec,webpdf,contemporary,medium,namedate]{oup-authoring-template}% uncomment this line for author year citations and comment the above
%\documentclass[unnumsec,webpdf,contemporary,medium]{oup-authoring-template}
%\documentclass[unnumsec,webpdf,contemporary,small]{oup-authoring-template}

@@

\usepackage[tablesonly,heads,nolists]{endfloat}

@@

%% Toggle with or without figures
\def\nofig{1}
